The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-13 methods/ms.tex
Add_to_header updated

\affil{{$^\casa$}{\it{CASA, University of Colorado, CB 389, Boulder, CO 80309}}}
%, \email{John.Bally@casa.colorado.edu}
%      \email{adam.ginsburg@colorado.edu}
%      \email{cara.battersby@colorado.edu}
%      \email{Jason.Glenn@colorado.edu} \email{pmh@astro.as.utexas.edu}
%      \email{Guy.Stringfellow@colorado.edu} }}

@@

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
area, systematic survey of the Northern Galactic Plane in the
(sub)millimeter continuum without pre-selected targets.  The survey
has detected \ncores\ clumps to a limiting depth of between
\bgpsdepthlow\ and \bgpsdepthhigh\ mJy RMS.  We include maps of 100
contiguous square degrees from $l=-10.5$ to $l=86.5$ and $b=\pm0.5$
with a resolution of 31\arcsec, as well as regions in IC1396, $l=111$
(NGC7538), W3/4/5, and Gem OB1.  The most striking feature of the maps
is the filamentary structure of cold dust throughout the Galaxy.

>>>>

\affil{{$^\casa$}{\it{CASA, University of Colorado, CB 389-UCB, Boulder, CO 80309}}}
%, \email{John.Bally@casa.colorado.edu}
%      \email{adam.ginsburg@colorado.edu}
%      \email{cara.battersby@colorado.edu}
%      \email{Jason.Glenn@colorado.edu} \email{pmh@astro.as.utexas.edu}
%      \email{Guy.Stringfellow@colorado.edu} }}

@@

We present the Bolocam Galactic Plane Survey (BGPS), a 1.1 mm
continuum survey of \bgpsarea\ square degrees of the Galactic Plane in
the 1st, 2nd, and 3rd quadrants.  The BGPS represents the first large
area, systematic survey of the Northern Galactic Plane in the
millimeter continuum without pre-selected targets.  The survey
has detected \ncores\ clumps to a limiting depth of between
\bgpsdepthlow\ and \bgpsdepthhigh\ mJy RMS.  We include maps of 100
contiguous square degrees from $l=-10.5$ to $l=86.5$ and $b=\pm0.5$
with a resolution of 31\arcsec, as well as regions in IC1396, $l=111$
(NGC7538), W3/4/5, and Gem OB1.  The most striking feature of the maps
is the filamentary structure of cold dust throughout the Galaxy.
